%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.7in,top=0.4in,right=0.7in,bottom=0.5in]{geometry} % Document margins
\usepackage{hyperref} % For clickable links

%----------------------------------------------------------------------------------------
%   DOCUMENT START
%----------------------------------------------------------------------------------------
\name{Vinicius Saturnino} % Your name
\address{+55 061 98347-1148 \\ Brasília, Federal District, Brazil \\ \href{mailto:viniciussaturnino78@gmail.com}{viniciussaturnino78@gmail.com}} % Contact
\address{\href{https://github.com/viniciussaturnino}{github.com/viniciussaturnino} \\ \href{https://linkedin.com/in/viniciussaturnino07}{linkedin.com/in/viniciussaturnino07}} % Social links
\begin{document}

%----------------------------------------------------------------------------------------
%   ABOUT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{About}

\begin{rSubsection}{}{}{}{}
\item Software Engineer with a solid academic background from the University of Brasilia (UnB), specialized in architecting high-performance 
distributed systems with a focus on Backend and DevOps. Expert-level proficiency in Python (Django, FastAPI, Flask) and Node.js to build scalable 
infrastructure. With hands-on experience in AWS and GCP, I bridge the gap between development and infrastructure, optimizing cloud environments 
through Kubernetes, Kafka, and Terraform to ensure security, high availability, and cost-efficiency.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{WEX}{Feb. 2025 -- Present}{Software Development Engineer}{}

\item \textbf{Kafka as a Service (KaaS)}: Engineer within the PaaS division, providing high-scale streaming infrastructure for global business 
units, including Health \& Benefits and PCI products.

\item \textbf{Compliance-Driven Encryption Gateway}: Architected a transparent encryption layer using Conduktor Gateway and BYOC to automate 
PHI and PII protection. This solution ensures strict HIPAA and PCI DSS compliance by encrypting sensitive data at the tenant level.

\item \textbf{Security \& Governance}: Implemented "security-by-default" protocols, allowing product teams to process sensitive messaging 
workloads without manual encryption logic, reducing data breach risks and streamlining regulatory audits.

\item \textbf{Infrastructure Automation}: Developed a Python-based CLI tool to manage user access and Kafka configurations via Kubernetes and 
Terraform, ensuring full operational traceability through Kafka events.

- Tech Stack: Kafka, Kubernetes, Terraform, Python, Go, AWS, Docker, GitHub Actions, Conduktor.
\end{rSubsection}

\begin{rSubsection}{Pilar}{May. 2024 -- Feb. 2025}{Software Engineer}{}

\item \textbf{System Architecture}: Engineered a high-impact lead management system using Python (Flask), driving agent partnership growth and revenue.

\item \textbf{Scalability \& Performance}: Deployed and managed scalable cloud resources on AWS, implementing advanced monitoring with Sentry and New 
Relic to maintain high availability.

\item \textbf{Operational Excellence}: Automated end-to-end delivery by integrating CI/CD pipelines, ensuring seamless updates and robust code quality through Pytest.

\item \textbf{Engagement Tools}: Designed and implemented a comprehensive real-time notification engine to manage complex partnership lifecycles and 
property alerts.

- Tech Stack: Docker, AWS, Agile, Lint, MongoDB, Grafana, Sentry, New Relic.
\end{rSubsection}

\begin{rSubsection}{Tembici}{Mar. 2022 -- Feb. 2024}{Software Engineer}{}

\item \textbf{Financial Infrastructure}: Orchestrated the development of an internal Payment Gateway from scratch using Django Rest Framework, migrating over 60\% 
of invoice processing in-house.

\item \textbf{International Expansion}: Led the integration of a cross-border Payment Hub (Yuno), enabling transactions in Colombia, Chile, and Argentina 
while reducing fees.

\item \textbf{Event-Driven Architecture}: Built reliable payment services using GCP (Pub/Sub, Cloud Functions) and PostgreSQL, ensuring fault tolerance 
and real-time processing.

\item \textbf{Innovation \& Leadership}: Developed and presented high-stakes POCs using FastAPI and React to stakeholders, leading the 
full-scale implementation of new payment methods like PIX (Adyen).

- Tech Stack: Docker, AWS, GCP, Agile, Lint, SQL, Terraform, Cloud Monitoring, NewRelic, Sentry, Unleash.
\end{rSubsection}

\begin{rSubsection}{Zapay}{Sep. 2021 -- Mar. 2022}{Software Engineer}{}

\item \textbf{Fullstack Development}: Delivered robust web solutions using Python (Django, FastAPI) and React, maintaining high code standards 
through rigorous unit and integration testing.

\item \textbf{Messaging \& Reliability}: Implemented event-driven services using RabbitMQ (AMQP) to ensure decoupled and reliable communication between 
microservices.

\item \textbf{Financial Reconciliation}: Developed internal systems tailored for finance teams to automate and streamline bill and invoice reconciliation.

\item \textbf{Agile Collaboration}: Actively contributed to the full Software Development Lifecycle within a Scrum framework, utilizing 
Gitflow to ensure stable production pipelines and continuous delivery.

- Tech Stack: Docker, AWS, Agile, Lint.
\end{rSubsection}

% \begin{rSubsection}{Instabuy}{Jun. 2021 -- Oct. 2021}{Backend Developer}{}
% \item Development of APIs integration projects using Python to online sell/delivery market. Write unit tests using pytest to cover up all system. \\
% - Tech Stack: Kanban, Agile, Lint, Pytest, AWS, Docker.
% \end{rSubsection}

% \begin{rSubsection}{Lead Up}{May. 2021 -- Jun. 2021}{Backend Developer}{}
% \item Backend development using Javascript/Typescript Frameworks (Express, NestJS). \\
% - Tech Stack: Docker, AWS, Lint, Agile.
% \end{rSubsection}

% \begin{rSubsection}{Federal General Accounting Office (TCU)}{Mar. 2021 -- Oct. 2021}{Intern}{}
% \item Worked on a page to receive and redirect of demands performed by Federal General Accounting Office (TCU) ombudsman using SQL/PLSQL. \\
% - Tech Stack: Oracle, SQL, APEX.
% \end{rSubsection}

% \begin{rSubsection}{Ai.Lab UnB}{Mar. 2020 -- Sep. 2020}{Researcher}{}
% \item Development of projects and automation to work with Machine Learning fundamentals.  \\
% - Tech Stack: Docker, Tensorflow, Pandas.
% \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Bachelor of Software Engineering}{Aug. 2018 -- Jul. 2024}{University of Brasília (UnB)}{}
%\vspace{-.1cm}
%Overall GPA: 78\%
\vspace{-.65cm}
\item[]
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%   Technical Experience 
%----------------------------------------------------------------------------------------

% \begin{rSection}{Projects}

% \begin{rSubsection}{Schedula - have your issues schedule in one platform}{Nov. 2022 -- Mar. 2023}{University of Brasília - Class: Software Product Engineering}{}
% \item NestJS services development.
% \item NextJS client development.
% \item Microservices development.
% - Tech Stack: Docker, Makefile, SonarCloud, Jupyter Notebook, CI/CD, Jest, Agile.
% \end{rSubsection}

% \begin{rSubsection}{Garimpei - Sell your used stuff online!}{Mar. 2022 -- Apr. 2022}{University of Brasília - Class: Software Design Architeture}{}
% \item FastAPI services development.
% \item NestJS services development.
% \item NextJS client development.
% \item Microservices development.
% - Tech Stack: Docker, Makefile, Agile.
% \end{rSubsection}

% \begin{rSubsection}{Lend.It - Already helped your neighbor today?}{Mar. 2021 -- Jun. 2021}{University of Brasília - Class: Software Methods}{}
% \item Flask services development.
% \item Express services development.
% \item Flutter application development.
% \item Microservices development.
% - Tech Stack: Docker, Makefile, Agile.
% \end{rSubsection}

% \end{rSection}

%----------------------------------------------------------------------------------------
%   LICENSES SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Licenses \& Certifications}

% \begin{rSubsection}{Ignite}{Jul. 2021}{Rocketseat}{}
% %\vspace{-.1cm}
% %Overall GPA: 78\%
% \vspace{-.65cm}
% \item[]
% \end{rSubsection}

% \begin{rSubsection}{English Conversation}{Nov. 2024}{Cambly}{}
% %\vspace{-.1cm}
% %Overall GPA: 78\%
% \vspace{-.65cm}
% \item[]
% \end{rSubsection}

% \end{rSection}

% %----------------------------------------------------------------------------------------
% %   TECHNICAL SKILLS SECTION
% %----------------------------------------------------------------------------------------
% \iffalse
\begin{rSection}{Technical Skills}
    \small{\item{
     \textbf{Programming Languages}{: Python (Django, FastAPI, Flask), JavaScript/TypeScript (Node.js, Nest.js, React), Go, SQL.} \\
     \textbf{Cloud Platforms}{: Amazon Web Services (AWS), Google Cloud Platform (GCP).} \\
     \textbf{DevOps \& Infrastructure}{: Kubernetes, Kafka (KaaS), Docker, Terraform, RabbitMQ, GitHub Actions, CI/CD Pipelines.} \\
     \textbf{Data \& Databases}{: PostgreSQL, MongoDB, BigQuery, Amazon S3, Event-Driven Architecture.} \\
     \textbf{Observability \& Tools}{: Sentry, New Relic, Grafana, Datadog, Prometheus, Unleash, Gitflow, Agile/Scrum.}
    }}
\end{rSection}

% %----------------------------------------------------------------------------------------
% %   LANGUAGES SECTION
% %----------------------------------------------------------------------------------------
% \iffalse
\begin{rSection}{Languages}
    \small{\item{
     \textbf{Portuguese}: Native Speaker \\
     \textbf{English}: Professional Working Proficiency (100+ hours of conversation with native speakers). \href{https://www.cambly.com/en/certificate/verify/778478f1}{\textbf{Certificate URL}}
    }}
\end{rSection}

\end{document}
